Phenotypes_Planting_2019

### 2020-03-01 analysis/common-garden-allele-balancing/2_allele_frequencies_common_gardens.Rmd

```{r}
loss_freq %>%
    filter(Loss_BRKG > 75 | Loss_LINC > 78 | Loss_FRMI > 54 | 
             Loss_CLMB > 51) %>% 
  mutate(Loss_freq = (Loss_BRKG/MAC_BRKG_2018 + Loss_FRMI/MAC_FRMI_2018 +
                            Loss_LINC/MAC_LINC_2018 +
                            Loss_CLMB/MAC_CLMB_2018)/4) %>% 
  ggplot(aes(x = POS/1000000, y = Loss_freq)) + 
  geom_hex() + 
  facet_wrap(~CHR, scales = "free_x", nrow = 1) + 
  scale_fill_viridis(trans = "log10") + 
  xlab("Position (Mb)") + ylab("Minor Allele Loss") +
  theme(legend.position = "right", 
        axis.text.x = element_text(angle = 45, hjust = 1))
save_plot(filename = "Distribution_of_SNPs_1per_delta_one_lost_all_four_sites.png", plot = last_plot(), base_asp = 4, base_height = 4)
frz_freq %>%
  filter(Loss_BRKG > 159 | Loss_LINC > 179 | Loss_FRMI > 84 | 
           Loss_CLMB > 94) %>%
  mutate(Loss_freq = (Loss_BRKG/MAC_BRKG_2018 + Loss_FRMI/MAC_FRMI_2018 +
                            Loss_LINC/MAC_LINC_2018 +
                            Loss_CLMB/MAC_CLMB_2018)/4) %>% 
  ggplot(aes(x = POS/1000000, y = Loss_freq)) +
  geom_hex() + 
  facet_wrap(~CHR, scales = "free_x", nrow = 1) + 
  scale_fill_viridis(trans = "log10") + 
  xlab("Position (Mb)") + ylab("Minor Allele Loss") +
  theme(legend.position = "right", 
        axis.text.x = element_text(angle = 45, hjust = 1))
save_plot(filename = "Distribution_of_SNPs_1per_delta_all_four_sites.png", plot = last_plot(), base_asp = 4, base_height = 4)
```

>>>>

```{r}
loss_freq %>%
    filter(Loss_BRKG > 75 | Loss_LINC > 78 | Loss_FRMI > 54 | 
             Loss_CLMB > 51) %>% 
  mutate(Loss_freq = (Loss_BRKG/MAC_BRKG_2018 + Loss_FRMI/MAC_FRMI_2018 +
                            Loss_LINC/MAC_LINC_2018 +
                            Loss_CLMB/MAC_CLMB_2018)/4) %>% 
  ggplot(aes(x = POS/1000000, y = Loss_freq)) + 
  geom_hex() + 
  facet_wrap(~CHR, scales = "free_x", nrow = 1) + 
  scale_fill_viridis(trans = "log10") + 
  xlab("Position (Mb)") + ylab("Minor Allele Loss") +
  theme(legend.position = "right", 
        axis.text.x = element_text(angle = 45, hjust = 1))
save_plot(filename = "Distribution_of_SNPs_1per_delta_one_lost_all_four_sites.png", plot = last_plot(), base_asp = 4, base_height = 4)
frz_freq %>%
  filter(Loss_BRKG > 159 | Loss_LINC > 179 | Loss_FRMI > 84 | 
           Loss_CLMB > 94) %>%
  mutate(Loss_freq = (Loss_BRKG/MAC_BRKG_2018 + Loss_FRMI/MAC_FRMI_2018 +
                            Loss_LINC/MAC_LINC_2018 +
                            Loss_CLMB/MAC_CLMB_2018)/4) %>% 
  ggplot(aes(x = POS/1000000, y = Loss_freq)) +
  geom_hex() + 
  facet_wrap(~CHR, scales = "free_x", nrow = 1) + 
  scale_fill_viridis(trans = "log10", option = "B") + 
  xlab("Position (Mb)") + ylab("Minor Allele Loss") +
  theme(legend.position = "right", 
        axis.text.x = element_text(angle = 45, hjust = 1))
save_plot(filename = "Distribution_of_SNPs_1per_delta_all_four_sites.png", plot = last_plot(), base_asp = 4, base_height = 4)
```

### 2020-03-01 data-raw/phenotypes_2019.Rmd

load("../data/sites.rda")
load("../data/metadata.rda")
load("../data/Taxa.rda")

@@

Use long format data to look for outlier values. This data has associated plot positions (PLOT_GL and PLOT_LC), as well as all associated notes (on greenup, flowering, harvest, chlr and spad). The notes might be relevant for outlier analysis.

@@

>>>>

load("../data/sites.rda")
load("../data/metadata.rda")
meta732 <- read_csv("~/Github/pvdiv-climate-gwas/data/Metadata_2020-02.csv")
meta732 <- meta732 %>%
  add_row(PLANT_ID = "AP13", LIBRARY = "REF", Genetic_subpop_50per = "Texas", Genetic_subpop_95per = "Texas", Ecotype = "Texas", Texas_Q = 1, Eastcoast_Q = 0, Midwest_DA = 0, LIB_GROWN = "Y")

load("../data/Taxa.rda")

@@

Use long format data to look for outlier values. This data has associated plot positions (PLOT_GL and PLOT_LC), as well as all associated notes (on greenup, flowering, harvest, chlr and spad). The notes might be relevant for outlier analysis.
```{r}
load("~/Github/pvdiv-phenology-gxe/data/phenotypes_2019.rda")

phenotypes_long_2019 <- phenotypes_wide_2019 %>%
  pivot_longer(cols = BRKG_BIOMASS:TMPL_TC_EOS, names_to = "SITE_PHE", values_to = "Value") %>%
  separate(col = "SITE_PHE", into = c("SITE", "_", "PHE"), sep = c(4,5), remove = FALSE) %>%
  dplyr::select(-"_")
```

@@

### BIOMASS

```{r}
meta732$Genetic_subpop_50per <- factor(meta732$Genetic_subpop_50per, levels = c("Texas", "Eastcoast", "Midwest"))

phenotypes_long_2019 %>%
  filter(grepl("BIOMASS", PHE)) %>%
  left_join(meta732, by = "PLANT_ID") %>%
  filter(!(Genetic_subpop_50per %in% c("Admixed", "NA")), !is.na(Genetic_subpop_50per)) %>%
  ggplot(aes(x = Value)) +
  geom_histogram(aes(fill = Genetic_subpop_50per), binwidth = 500) + 
  facet_grid(SITE~PHE, scales = "free_y") +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = -1) +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1)) + xlab("Value") + ylab("Count of Individuals") +
  geom_vline(xintercept = 2800, linetype = 3) +
  scale_y_continuous(breaks = c(10, 50, 100))

save_plot("2019_Phenotypic_Data_by_Site_and_Genetic_Subpop_scale_2020-02-14.png", plot = last_plot(), base_height = 7, base_asp = 0.4)
